Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-11-24 Moltres.tex
Updated information about BW XK7 node
Taken in from NCSA site: https://bluewaters.ncsa.illinois.edu/node_core_comparison

We conducted strong and weak scaling studies to characterize parallel 
performance in Moltres.
In case of strong scaling, the problem size remains fixed but the number of
processors is increased. Strong scaling studies seek to identify an
optimal ratio between the number of processors and elements for the most
rapid and power-efficient computation for a given problem. We measured
Moltres strong scaling with a simple 2D axisymmetric
case for various problem sizes separately for intra-node (2,820; 5,640;
11,280 and 28,200 elements) and extra-node (86,655; 173,310; 317,735;
664,355 elements) setup on Blue Waters' XK7 nodes (1 AMD 6276 Interlagos 
CPU, 16 integer scheduling units, 32 virtual units, nominal clock speed
2.3 GHz).

>>>>

We conducted strong and weak scaling studies to characterize parallel 
performance in Moltres.
In case of strong scaling, the problem size remains fixed but the number of
processors is increased. Strong scaling studies seek to identify an
optimal ratio between the number of processors and elements for the most
rapid and power-efficient computation for a given problem. We measured
Moltres strong scaling with a simple 2D axisymmetric
case for various problem sizes separately for intra-node (2,820; 5,640;
11,280 and 28,200 elements) and extra-node (86,655; 173,310; 317,735;
664,355 elements) setup on Blue Waters' XK7 nodes (two AMD 6276 Interlagos 
CPU per node, 16 floating-point bulldozer core units per node or 32 "integer"
cores per node, nominal clock speed is 2.3 GHz).
